
% -------------------------------------------------------
%  English Abstract
% -------------------------------------------------------


\pagestyle{empty}

\begin{latin}

\begin{center}
\textbf{Abstract}
\end{center}
\baselineskip=.8\baselineskip
There has been lots of research in Geometry Optimization. One of the most important instances of them is $k$-centers problem, which is in $NP$-Hard problems family. In this thesis, we focus on a subset of geometry optimization problems (included $k$-centers) in Sliding Window model. The sliding window model is driven from Data Stream model which every input arrives one by one and the space is very limited. The main diffrenece of these two models is that in the sliding window we are interested in the $N$ latest points not all of the arrived points.

In this thesis, we study Minimum Enclosing Ball, $2$-centers in two dimensions space and Euclidean $k$-centers in Sliding Window model. We provide a $(1+\eps)$-approx algorithm  for MEB in $d$-dimensions. To our knowledge there is no well known algorithm for MEB in $d$-dimensions where $d >2 $. We also provide a $(1+\eps)$-approx algorithm for $2$-centers in $2$-dimensions, which improves the previous $(4+\eps)$-approx algorithm.
At last we study $k$-centers problem and provide a $(2+\eps)$-approx algorithm for it. Our algoithm improves the previous $(6+\eps)$-approx algorithm which was designed for metric space. The space complexity is $\text{poly}(R, d, \frac{1}{\epsilon^d})$. The $R$ denotes the
“spread” of the point set or the ratio of maximum result to minimum distance of any two points in the window.



\bigskip\noindent\textbf{Keywords}:
Geometry Optimization, Sliding Window, Approximation Algorithms, Massive Data

\end{latin}

\newpage
